Enhancing Software Development with Artificial Intelligence

### 2023-09-10 Generative Software/proposal2.tex
WIP

\begin{abstract}
    This proposal aims at supporting software engineers to develop software correctly and reliably by construction.
    The threshold of learning formal specification languages has kept scores of software engineers from using them in practice.
    Recent progress in Artificial Intelligence fuels the hope that AI might leverage the use of formal specification languages.
    This proposal aims at investigating how.

@@

   This capability offers the following benefits:
\begin{itemize}
    \item By generating software, we can produce live demonstrations periodically to keep the future user population informed of the progress.
    This produces quick results, which keeps funders happy.
    \item By automating software production, we can prevent a large class of mistakes and thereby reduce the project risk.
    \item By formally specifying the functionality, we can give valuable guarantees on the correctness of the results.
    \item Software that is correctly generated needs no testing. This yields significant savings on testing and test maintenance.
    \item The tooling that has been developed at the Open University is especially suitable for automating business processes and workflows.
\end{itemize}

>>>>

\begin{abstract}
    This proposal aims at supporting software engineers to develop software correctly and reliably by construction.
    The threshold of learning specification languages has kept scores of software engineers from using them in practice.
    Recent progress in Artificial Intelligence fuels the hope that AI might leverage the use of specification languages.
    This proposal aims at investigating how.

@@

   We expect the following benefits:
\begin{itemize}
    \item By generating software, we can produce live demonstrations periodically to keep the future user population informed of the progress.
    This produces quick results, which keeps funders happy.
    \item By automating software production, we can prevent a large class of mistakes and thereby reduce the project risk.
    \item By formally specifying the functionality, we can give valuable guarantees on the correctness of the results.
    \item Software that is correctly generated needs no testing. This yields significant savings on testing and test maintenance.
    \item The tooling that has been developed at the Open University is especially suitable for automating business processes and workflows.
\end{itemize}
